---
title: "HW4_koopmann"
author: "Michael Koopmann"
date: "2/23/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Question Set 1:

```{r cars}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)

summary(choco$Rating)
```
1) There are 1852 chocolate bars rated with the Mean rating of 3.191

2) Plot of number of reports by year

```{r pressure, echo=FALSE}
library(ggplot2)
library(scales)

ggplot(choco, aes(x = Review.Date)) + geom_bar(position='dodge', colour='black') + scale_x_continuous(breaks = pretty_breaks()) + labs(title = "Reviews per Year")

```

Question Set 2:

1)
```{r}
ggplot(choco, aes(x = Rating)) + geom_histogram(bins = 17, colour="black", fill="white")
```
The graph shows high concentration of ratings between 2.5 and 4 and the sharp drop off after 4 and the few 5 ratings.  Our Q1 is at 3 and Q3 is 3.5 so the range is .5 so all the ratings below 2.25 are outliers along with the marking at 5.

2)
```{r}
ggplot(choco, aes(x = Cocoa.Pct, y = Rating)) + geom_jitter()
```
No I don't see any trend within the plot theres lower percentage with the same rating as higher percentage.  I will say that ideal range seems to be between 60 and 80 percentage.


3)
```{r}
subchoco <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))
ggplot(subchoco, aes(x = Company.Location, y = Rating))+
  geom_boxplot()+
  coord_flip()+
  ylab("Rating")
```
All 3 locations have a similiar mean but Canada has a larger upper quantile  about double of France and USA which have similiar upper quantile.  Also USA has a larger lower quantile which is about double France and Canada which have similiar lower quantile.  All 3 upper adjacent goes to 4 but the lower adjacent of France only goes to 2.5 while Cananda and USA goes to 2.  From this I'd say that France has better consistency of having a higher rating but Canada upper quantile being larger makes me say that they have the best ratings.

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
